\large Neural, Tree, and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-06-25 docs/papers/sto/so.tex
FIXUP draft: minor reorg of SO subsection

@@

In Fourier space, the gravitational force field reads
\begin{equation}
- i \vk \varphi(\vk) = i \frac32 \Omegam H_0^2 \,\frac{\vk}{k^2} \delta(\vk),
\end{equation}
Force sharpening
%
\begin{equation}
\frac{i k_i}{k^2} \to \frac{i k_i}{k^2}
  f(k_i; \vvartheta) g(k_1, k_2, k_3; \vvartheta),
\end{equation}
%
where $f$, $g$ are neural networks, each approximating a nonlinear
function of the wavevector components and all the features considered
above in dimensionless combinations, e.g.,
%
\begin{equation}
f(k_i; \vvartheta) = f(k_i/k_P, kR_\tophat, \cdots; D, f, \cdots).
\end{equation}
%
$f$ and $g$ are optimized during training to correct and sharpen the
gravitational forces.
Gravity obeys the $\mathrm{O}(3)$ rotational symmetry, which is however
broken by the PM solver to the O\textsubscript{h} discrete symmetry with
48 elements involving permutations and reversals of the 3 principal axes
of the simulation box.
The PM evaluation of each force component can further break the symmetry
along that axis, leaving the remaining 2 permutationally symmetric.
Therefore, we implement $f$ and $g$ to be even functions of the
wavevector components, and $g$ to be permutation equivariant in all 3
components, so that $f g$ is the most general modification to the force
kernel.
An even and real kernel in configuration space is also even in Fourier
space.
We take the absolute value for the evenness, and sort the 3 wavevector
compontents to achieve the permutation equivariance.

>>>>

In Fourier space, the gravitational force field reads
\begin{equation}
- i \vk \varphi(\vk) = i \frac32 \Omegam H_0^2 \,\frac{\vk}{k^2} \delta(\vk),
\end{equation}
Force sharpening
%
\begin{equation}
\frac{i k_i}{k^2} \to \frac{i k_i}{k^2}
  f(k_i; \vvartheta) g(k_1, k_2, k_3; \vvartheta),
\end{equation}
%
where $f$, $g$ are neural networks, each approximating a nonlinear
function of the wavevector components and all possible relevant features
$\vvartheta$ summarized in \autoref{tab:feat} and discussed below.

@@

Dimensionless combinations, e.g.,
%
\begin{equation}
f(k_i; \vvartheta) = f(k_i/k_P, kR_\tophat, \cdots; D, f, \cdots).
\end{equation}
%
$f$ and $g$ are optimized during training to correct and sharpen the
gravitational forces.
Gravity obeys the $\mathrm{O}(3)$ rotational symmetry, which is however
broken by the PM solver to the O\textsubscript{h} discrete symmetry with
48 elements involving permutations and reversals of the 3 principal axes
of the simulation box.
The PM evaluation of each force component can further break the symmetry
along that axis, leaving the remaining 2 permutationally symmetric.
Therefore, we implement $f$ and $g$ to be even functions of the
wavevector components, and $g$ to be permutation equivariant in all 3
components, so that $f g$ is the most general modification to the force
kernel.
An even and real kernel in configuration space is also even in Fourier
space.
We take the absolute value for the evenness, and sort the 3 wavevector
compontents to achieve the permutation equivariance.
